\documentclass[12pt]{cavender_cv}
\usepackage{hanging}

\begin{document}

\vspace{16pt}
\name{Kenyon Paul Cavender}
%\contact{kenyoncavender@gmail.com}
%\contact{(979) 492-9135}
\vspace{25pt}

\hspace{-.75cm}\begin{minipage}[t]{0.65\textwidth}
\section{Objective}
I am a graduate student at MSU working 
towards a master's degree in Statistics.
The work I am most interested in involves
societal problems that can be solved or
more accurately understood through the use 
of statistical modeling. 
\subsecspace 

\section{Work Experience}
\subsection{RATPDev USA - Austin, TX}
\textbf{Independent Contractor / Analyst} \hfill Current 
\begin{hangparas}{.25in}{1}

-- Systems efficiency analysis - find wasted resources
in over 30 transit contracts in the US.

-- Financial modeling - develop checks for our contract
bidding process.

-- Data collection - standardize KPI reporting 
among all contracts. 

-- Data visualization - develop graphic representations
of essential metrics. 

-- Route optimization - find inefficiencies in route
scheduling.
\end{hangparas}
\vspace{4pt}

\textbf{Data Analyst} \hfill 2016 - 2019 
\begin{hangparas}{.25in}{1}

-- Task automation - reduced redundant time expenditure
for daily/weekly/monthly reports.

-- Resource management - managed a \$2MM  parts inventory
to increase essential parts availability while reducing 
costs.

-- API development - developed a system to connect the 
asset management software to our invoicing software.
\end{hangparas}

\subsecspace

\subsection{Paisano Energy, LLC - Dallas, TX}
\textbf{Analyst} \hfill 2015 to 2016
\begin{hangparas}{.25in}{1}

-- Modeled the economic performance of oil fields 
as determined by reservoir performance, fluctuating
operating expenses, and abnormal energy content of 
natural gas.

-- Gathered and compiled geological, economic, and 
legal data on mineral estates.

-- Modeled ROI analysis on mineral interest 
transactions and recommended purchases to principal 
investors.

\end{hangparas}
\subsecspace

\section{Publication}
Cavender, K. L., Graham, J. E., Fox, R. P., Flynn, 
R., \& Cavender, K. P. (2016). Body Language: 
Toward an Affective Formalism of \textit{Ulysses}. 
In S. Ross \& J. O’Sullivan (Eds.), \textit{Reading 
Modernism with Machines: Digital Humanities 
and Modern Literature}. Basingstoke, United Kingdom: 
Palgrave Macmillan. 
\subsecspace

\end{minipage}%
\hspace{.75cm}\begin{minipage}[t]{0.25\textwidth}

\section{Education}
\subsection{Michigan State University}
\vspace{-4pt}
M.S. in Statistics \\
Currently Enrolled

\subsecspace

\subsection{Texas A \& M University}
\vspace{-4pt}
B.S. in Mathematics \\
Graduated Dec 2014

\subsecspace

\section{Contact Information}
\subsection{Address}
\vspace{-4pt}
1031 Daisy Ln Unit 3 \\
East Lansing, MI \\
48823

\subsecspace

\subsection{Email}
\vspace{-4pt}
kenyoncavender@gmail.com

\subsecspace

\subsection{Phone Number}
\vspace{-4pt}
(979) 492-9135

\subsecspace


\section{Technical Skills}
\subsection*{Proficient}
-- Data visualization \\
-- Python \\
-- R \\
-- SQL \\
-- Linux/Unix \\


\subsection*{Competent}
-- C/C++ \\
-- JavaScript \\
-- Task automation \\
-- Public speaking \\


\end{minipage}

\end{document}
