\documentclass[12pt, oneside, letterpaper]{notes}

\begin{document}
\title{Class Notes for STT861}
\author{Kenyon Cavender}
\date{2019 - 09 - 01}
\maketitle

\section{Lecture One}

\begin{myex}
  Toss a fair coin; what is the probability of obtaining heads? 
  $P(H) = \frac{1}{2}$
\end{myex}

\begin{myex}
  Throw a fair die; what is the probability of obtaining 6?  
  What about obtaining an even number? \\
\indent$P(6) = \frac{1}{6}$ \\
\indent$P(n = 2,4,6) = \frac{1}{2}$ 
\end{myex}

\paragraph{}
  The probability is not the realized result, but the 
  convergence of results as the number of iterations approaches 
  infinity.  Review the Weak Law of Large Numbers.

\begin{mydef}
  A \textbf{random experiment} is an action which will result 
  in one of the many possible outcomes. 
\end{mydef}

\begin{mydef}
  A \textbf{sample space} is the collection of all possible 
  outcomes of a random experiment.  We shall denote by \textbf{S}.
\end{mydef}

\begin{mydef}
  A \textbf{set} is a collection of some \underline{well defined} 
  objects.
\end{mydef}

\begin{mydef}
  \textbf{Outcomes} are also called \textbf{sample points}.
\end{mydef}

\begin{mydef}
  An \textbf{Event} is a subset of sample space \textbf{S} for 
  which we can define probability.
\end{mydef}

\begin{mydef}
  Suppose A and B are two sets.  $A \subset B$ (A is a 
  \textbf{subset} of B) if $x \in A$ implies $x \in B$. 
  If $A \subset B$ and $B \subset A$ then $A=B$.
\end{mydef}

\begin{mydef}
  A set is called an empty set (or \textbf{null set}) if it contains no elements.\\
  \indent Notation: $\{ \emptyset \}$ \\
  \indent Convention: $\emptyset \subset A$, for any set A \\
  \indent Corrolary: $\forall A, \: \emptyset \subset A \subset \textbf{S}$
\end{mydef}

\begin{mydef}
  \textbf{Complement} $A^c$ is the set such that $x \in A^c \Rightarrow x \notin A$.\\
  \indent In other words, $A^c = \{ x : x \notin A \}$ \\
  \indent Notation: $A^c \: or \: A' \: or \: \overline{A}$
\end{mydef}



\end{document}

























